Object-Oriented Internet - Azure Interoperability

### 2020-11-30 Latex/Manuscript.tex
Final review of the latex text #37
- improved `Abstract`

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. To deal with the network traffic propagation asymmetry or assets mobility the reactive interoperability relationship of the interconnected nodes is proposed. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the implementation of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.

      The proposals are backed by proof of concept reference implementations conforming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario. It is in contrast to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.

>>>>

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the implementation of the embedded gateway archetype has been implemented as a composable part of an existing OPC UA PubSub framework.

      The proposals are backed by proof of concept reference implementations confirming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario. It is in contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.
